\chapter{Conclusion}

A large part of the project was understanding channel behaviour and how this can be represented in a stochastic manner. This was used to get an understanding of how to measure a real world multipath environment. The statistics of the very deep fades that needs to be addressed in \gls{URLLC} had not been empirically tested, but assumed Rayleigh distributed based on extensions from existing measurements of fading.

A statistical method of estimating the number of samples needed to validate the measurement was used. It was found that for a confidence interval of $\pm 1dB$ with a 90\% confidence level, $4.04E+6$ independent samples was needed. Several statistical techniques to decrease the required amount of samples were investigated. As all these techniques require a change of the overall distribution, which is not feasible for real measurements, none of these could be used. The bootstrap method was found to be a useful method that can provide the confidence level and interval based on the measurements.

To obtain the required amount of samples the use of both spatial and temporal domains was necessary. To minimize the correlation between samples the needed separation was estimated based on a Rayleigh fading channel. This was found to be 0.4$\lambda$ in space and 25 MHz for the room that was measured. 

%To investigate the deep fades that needs to be dealt with to deliver an connection that fulfils the \gls{URLLC} conditions, requires an extensive amount of samples. Therefore the spatial and temporal domains has to be taken advantage of. To achieve this optimal frequency and space separation needed to be estimated

To validate the measurements of very deep fades an average SNR of 64 dB was required. This includes not only the level of expected fading, but a margin ensuring that the measurement is not distorted by noise. The high SNR together with the needed amount of samples means the measurement was quite time consuming. 

In the end a total of 4.18$E+6$ samples was collected. Analysis of the samples showed that the assumptions of a WSSUS channel could only be scarcely justified. Further more was it found that half of the samples was to correlated ending with an effective sample pool of 2.09$E+6$ samples. The result being that verification of the extensions for the Rayleigh fading model was correct to some degree, but it could not be verified to the needed levels for \gls{URLLC}. The model was verified down to a probability of 1E-5 with an error of (1.26$\pm$1.23) dB at a 90\% confidence level. \todo{change results}

Further work on this topic would include introducing a \gls{PA} or similar to the measuring setup, this allows for the TX and RX antennas to be space further apart, while simultaneously increasing the SNR giving a larger region to measure the fading. Investigation of using diversity gain to lower the needed SNR might also prove useful, as this method will ultimately be used in \gls{URLLC} to reduce outages.

%\textbf{General problem statement:}
%Design a measurement system that can handle very deep fades and a statistical method to process the data and compare to existing models used in URLLC channels.

%This can be further specified to a more technical problem statement: \todo{Where do these numbers come from and why do we have two statements just after each other?!?}

%Ascertain with 90\% confidence with a 1 dB (25\%) margin that in a multipath environment, the cumulative distribution function of the fading gain can be assumed to increase in a log log linear fashion between -50dB and -20dB.

%To this it is important to investigate the following points: 
%\begin{itemize}
%	\item Find connections between channel statistics and sample size.
%	\item Find the reasonable confidence interval based on the minimum required sample size.
%	\begin{itemize}
%	\item Look into if there is a way to reduce the amount of samples needed by using statistical techniques.
% 	\end{itemize}
%	\item Figure out how to obtain uncorrelated samples in space,time and frequency.
%	\item Balance the sample acquisition for available resources. 
%	\item Design  a measurement setup that can acquire the samples needed.
%	\item Specify a method to process the obtained channel measurements.
%	\item Analyse the measurement and link the results to the current assumptions.
%\end{itemize}