\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\#                   srsUE configuration file  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# RF configuration  \\
\#  \\
\# dl\_earfcn: Downlink EARFCN code.  \\
\# freq\_offset: Uplink and Downlink optional frequency offset (in Hz)  \\
\# tx\_gain: Transmit gain (dB).   \\
\# rx\_gain: Optional receive gain (dB). If disabled, AGC if enabled  \\
\#  \\
\# Optional parameters:   \\
\# nof\_rx\_ant:         Number of RX antennas (Default 1, supported 1 or 2)  \\
\# device\_name:        Device driver family. Supported options: "auto" (uses first found), "UHD" or "bladeRF" \\  
\# device\_args:        Arguments for the device driver. Options are "auto" or any string.   \\
\#                     Default for UHD: "recv\_frame\_size=9232,send\_frame\_size=9232"  \\
\#                     Default for bladeRF: ""  \\
\# \#time\_adv\_nsamples: Transmission time advance (in number of samples) to compensate for RF delay   \\
\#                     from antenna to timestamp insertion.   \\
\#                     Default "auto". B210 USRP: 100 samples, bladeRF: 27.  \\
\# burst\_preamble\_us:  Preamble length to transmit before start of burst.   \\
\#                     Default "auto". B210 USRP: 400 us, bladeRF: 0 us.   \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\

$[$rf$]$  \\
\# 759.6 MHz  \\
dl\_earfcn = 6310  \\
\# 801.3 MHz  \\
\#dl\_earfcn = 6253  \\
freq\_offset = 0  \\
tx\_gain = 40  \\
rx\_gain = 40  \\
  \\
\#nof\_rx\_ant = 1  \\
\#device\_name = auto  \\
\#device\_args = auto  \\
\#time\_adv\_nsamples = auto  \\
time\_adv\_nsamples = 65  \\
\#burst\_preamble\_us = auto  \\
  
  
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# MAC-layer packet capture configuration  \\
\#  \\
\# Packets are captured to file in the compact format decoded by   \\
\# the Wireshark mac-lte-framed dissector and with DLT 147.   \\
\# To use the dissector, edit the preferences for DLT\_USER to   \\
\# add an entry with DLT=147, Payload Protocol=mac-lte-framed.  \\
\# For more information see: https://wiki.wireshark.org/MAC-LTE  \\
\#  \\
\# enable:   Enable MAC layer packet captures (true/false)  \\
\# filename: File path to use for packet captures  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\

$[$pcap$]$  \\
enable = false  \\
filename = /tmp/ue.pcap  \\
  
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# Log configuration  \\
\#  \\
\# Log levels can be set for individual layers. "all\_level" sets log  \\
\# level for all layers unless otherwise configured.  \\
\# Format: e.g. phy\_level = info  \\
\#  \\
\# In the same way, packet hex dumps can be limited for each level.  \\
\# "all\_hex\_limit" sets the hex limit for all layers unless otherwise  \\
\# configured.  \\
\# Format: e.g. phy\_hex\_limit = 32  \\
\#  \\
\# Logging layers: phy, mac, rlc, pdcp, rrc, nas, gw, usim, all  \\
\# Logging levels: debug, info, warning, error, none  \\
\#  \\
\# filename: File path to use for log output  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\

$[$log$]$  \\
all\_level = warning  \\
all\_hex\_limit = 32  \\
\#filename = /tmp/ue.log  \\
filename = stdout  \\
  
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# USIM configuration  \\
\#  \\
\# algo: Authentication algorithm (xor/milenage)  \\
\# op:   128-bit Operator Variant Algorithm Configuration Field (hex)  \\
\# amf:  16-bit Authentication Management Field (hex)  \\
\# k:    128-bit subscriber key (hex)  \\
\# imsi: 15 digit International Mobile Subscriber Identity  \\
\# imei: 15 digit International Mobile Station Equipment Identity  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\

$[$usim$]$  \\
algo = xor  \\
op   = 63BFA50EE6523365FF14C1F45F88737D  \\
amf  = 9001  \\
k    = 00112233445566778899aabbccddeeff  \\
imsi = 001010123456789  \\
imei = 353490069873319  \\
  
$[$gui$]$  \\
enable = false  \\
  
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# Expert configuration options  \\
\#  \\
\# ue\_category:          Sets UE category (range 1-5). Default: 4   \\
\#  \\
\# prach\_gain:           PRACH gain (dB). If defined, forces a gain for the tranmsission of PRACH only.,   \\
\#                       Default is to use tx\_gain in $[$rf$]$ section.   \\
\# cqi\_max:              Upper bound on the maximum CQI to be reported. Default 15.   \\
\# cqi\_fixed:            Fixes the reported CQI to a constant value. Default disabled.  \\
\# snr\_ema\_coeff:        Sets the SNR exponential moving average coefficient (Default 0.1)  \\
\# snr\_estim\_alg:        Sets the noise estimation algorithm. (Default refs)  \\
\#                          Options: pss:   use difference between received and known pss signal,   \\
\#                                   refs:  use difference between noise references and noiseless (after filtering) \\  
\#                                   empty: use empty subcarriers in the boarder of pss/sss signal  \\
\# pdsch\_max\_its:        Maximum number of turbo decoder iterations (Default 4)  \\
\# attach\_enable\_64qam:  Enables PUSCH 64QAM modulation before attachment (Necessary for old   \\
\#                        Amarisoft LTE 100 eNodeB, disabled by default)  \\
\# nof\_phy\_threads:      Selects the number of PHY threads (maximum 4, minimum 1, default 2)  \\
\# equalizer\_mode:       Selects equalizer mode. Valid modes are: "mmse", "zf" or any   \\
\#                       non-negative real number to indicate a regularized zf coefficient.  \\
\#                       Default is MMSE.   \\
\# cfo\_integer\_enabled:  Enables integer CFO estimation and correction. This needs improvement \\ 
\#                       and may lead to incorrect synchronization. Use with caution.   \\
\# cfo\_correct\_tol\_hz:   Tolerance (in Hz) for digial CFO compensation. Lower tolerance means that   \\
\#                       a new table will be generated more often.   \\
\# time\_correct\_period:  Period for sampling time offset correction. Default is 10 (ue\_sync.c),   \\
\#                       good for long channels. For best performance at highest SNR reduce it to 1.  \\  
\# sfo\_correct\_disable:  Disables phase correction before channel estimation to compensate for   \\
\#                       sampling frequency offset. Default is enabled.   \\
\# sss\_algorithm:        Selects the SSS estimation algorithm. Can choose between   \\
\#                       {full, partial, diff}.   \\
\# estimator\_fil\_w:      Chooses the coefficients for the 3-tap channel estimator centered filter.  \\ 
\#                       The taps are $[$w, 1-2w, w$]$  \\
\# metrics\_period\_secs:  Sets the period at which metrics are requested from the UE.   \\
\#  \\
\# pregenerate\_signals:  Pregenerate uplink signals after attach. Improves CPU performance.  \\
\#  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\

$[$expert$]$  \\
phy.verbose          = error  \\
\#n\_id\_ncell           = 37  \\
nbiot\_r14            = false  \\
ue\_category          = nb1  \\
\#n\_id\_ncell           = 0  \\
prach\_gain          = 20  \\
\#cqi\_max             = 15  \\
\#cqi\_fixed           = 10  \\
\#snr\_ema\_coeff       = 0.1  \\
\#snr\_estim\_alg       = refs  \\
\#pdsch\_max\_its       = 4  \\
\#attach\_enable\_64qam = false\\  
nof\_phy\_threads     = 1  \\
\#equalizer\_mode      = mmse\\  
\#cfo\_integer\_enabled = false\\  
\#cfo\_correct\_tol\_hz  = 50  \\
\#cfo\_pss\_ema	     = 0.1  \\
cfo\_ema		     = 0.1  \\
time\_correct\_period = 0  \\
\#sfo\_correct\_disable = false \\ 
\#sss\_algorithm       = full  \\
\#estimator\_fil\_w     = 0.1  \\
\#pregenerate\_signals = false  \\
\#metrics\_csv\_enable = true  \\
\#metrics\_csv\_filename = /tmp/ue\_metrics.csv  \\
  
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#  \\
\# Manual RF calibration  \\
\#  \\
\# Applies DC offset and IQ imbalance to TX and RX modules.   \\
\# Currently this configuration is only used if the detected device is a bladeRF  \\
\#  \\
\# tx\_corr\_dc\_gain: TX DC offset gain correction  \\
\# tx\_corr\_dc\_phase: TX DC offset phase correction  \\
\# tx\_corr\_iq\_i: TX IQ imbalance inphase correction  \\
\# tx\_corr\_iq\_q: TX IQ imbalance quadrature correction \\ 
\# same can be configured for rx\_*  \\
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# \\  

$[$rf\_calibration$]$  \\
tx\_corr\_dc\_gain = 20  \\
tx\_corr\_dc\_phase = 184  \\
tx\_corr\_iq\_i = 19  \\
tx\_corr\_iq\_q = 97  \\
  
$[$mass$]$  \\
number\_of\_ue = 12 \\