\chapter*{Preface}\label{ch:forord}%\addcontentsline{toc}{chapter}{Forord}

%This bachelor project in Communication Systems has been carried out during the spring of 2016, by a group of three students from Electronics and IT at Aalborg University.
%
%The project regards the development of a communication link between a satellite in space and a ground station, as well as  the development of a prototype implementation of a software defined radio to be used in the link.
%%This report and the prototype described in the following is made by a group of three students on sixth semester "Electronics and IT" at Aalborg University.
%
%A general knowledge of electronic engineering and more specifically communication systems is needed to read the report.  
%
%References to sources are of the APA-style, i.e. of the type [\emph{source name/author's surname, year, optional page number}]. Sources are listed in a bibliography at the end of the report, and PDFs, datasheets etc. can be found in the attached ZIP-file. Figures without a source are made by the project group.% Appendices are listed after the bibliography.
%
%This report is organized in three parts. The first part is a technical analysis that goes in depth with antennas, a link budget of the communication link between a satellite and a ground station at AAU, different suitable modulation types and, finally, a requirements for a prototype of the radio to be used in the communication link is established. \\ In part two, the theory, simulation and implementation of the prototype is described. \\ Part three contains the test of the prototype related to the requirements set up for it in part 1. %Finally, part four contains descriptions of how two created antennas was made and descriptions of three test setups utilized in project and their related results.
%
%Special thanks should be addressed to PhD student Dereje Assefa and associate professor John Hansen for helping with the USRP's and LabVIEW. A thanks to assistant engineer Kristian Bank for helping with tests of the antennas in Starlab and for the great help regarding setting up and borrowing measurement equipment. Furthermore, a thanks goes to associate professors Flemming Bjerre Frederiksen and Carles Navarro Manchón for giving a helping hand in finding reading material.

The master thesis has been carried out between autumn 2017 and spring 2018, by two students from wireless communication system from Aalborg University.

Before reading the report it is advised to have a general understanding of either the LTE or NB-IoT protocol, as well as a fundamental understanding of cellular systems. 

References to sources are of the APA-style, i.e. of the type [\emph{source name/author's surname, year}]. Sources are listed in a bibliography at the end of the report. Figures without a source are made by the project group.% Appendices are listed after the bibliography.

The report starts with an introduction to the NB-IoT protocol before dividing the attention between two of the main domains in this technology: the energy consumption and the massiveness. In the end a discussion follows up on the findings in the report. The focus throughout the report is the design of an emulator, which can evaluate the protocol based on several parameters. Prior to the work done in this project, a project with a similar purpose has been done for the LTE protocol, some of the structure used for the emulator comes from the this project. Parallel with the this project Network and Distributed System group has been doing measurement of the battery lifetime of the NB-IoT protocol and a collaboration between the groups was established during the project.

Special thanks is addressed to Keysight Denmark, which has provided not only an industrial supervisor but also allowed access to their facilities including test equipment as well as providing access to source code of the baseline device emulator.


%%% stuff to mention in preface %%%%

% knowledge of LTE required











\vspace{0.5\baselineskip}\hfill Aalborg University, \today
\vfill

%% underskrifts afsnit %%

\vspace{1.5\baselineskip}
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.45pt}\\
  Mads Røgeskov Gotthardsen\\
 {\footnotesize mgotth13@student.aau.dk}
\end{minipage}
\vspace{1.5\baselineskip}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}
   Thomas Kær Juel Jørgensen\\
 {\footnotesize tkjj13@student.aau.dk}
\end{minipage}

}